Global patterns of forest autotrophic carbon fluxes

### 2020-01-31 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

```{r echo=FALSE, out.width='100%', fig.cap = "Map showing all data used in the analysis, coded by variable. Variables are plotted individually in Fig. S1. ", fig.pos='H'}
  knitr::include_graphics("distribution_all_variables_cropped.png")
```
*Data selection.* Over 50 variables of forest carbon stocks and annual fluxes are represented in the ForC database; this analysis focused on autotrophic carbon fluxes. Focal variables of this analysis are listed in Table 2.

@@

Within the ForC database, geographically proximate sites are clustered into geographic areas, with proximity defined using a hierarchical cluster analysis on the distance matrix of the sites and a cutoff of 25km. To account for correlations in measurements between tightly clustered sites, a random effect was specified as plot nested within geographic area.

>>>>

```{r echo=FALSE, out.width='100%', fig.cap = "Map showing all data used in the analysis, coded by variable. Variables are plotted individually in Fig. S1. ", fig.pos='H'}
  knitr::include_graphics("distribution_all_variables_cropped.png")
```
*Data selection.* This analysis focused on nine autotrophic carbon fluxes included in the ForC database (Table 2). These were selected based on *...*. The ForC database contains annual flux estimates, associated to plots, each with associated data on stand age and known history of disturbance and management, and, more broadly, sites (**Define**). Geographically proximate sites are clustered into geographic areas, with proximity defined using a hierarchical cluster analysis on the distance matrix of the sites and a cutoff of 25km [@anderson-teixeira_forc_2018].

@@

To account for correlations in measurements between tightly clustered sites, a random effect was specified as plot nested within geographic area.
